Object-Oriented Internet - Azure Interoperability

### 2020-10-08 Latex/Manuscript.tex
Work out Markdown\40.OOITechnologyFeatures.md #28
- convert to latex - minor changes
 - current .pdf generated.

Deployment of the hybrid solution providing interoperability of the
\textbf{machine-centric} cyber-physical systems designed atop of M2M
reactive communication and emerging cloud computing as a
\textbf{human-centric} front-end requires decisions addressing the
selection of the services supporting web user interface capable to
expose real-time process data. In this context, the service is any
autonomous (with own identity) software component or module that is
interfacing with selected cyber-physical systems for data collection,
analysis, and also remote control. Microsoft Azure is a cloud-based
product. It offers a vast variety of services. This virtual environment
handles an unlimited number of users and devices organized using a
solution concept. The solution aggregates users, devices, services, and
required additional resources scoping on a selected scenario. The
solution serves as a context that provides a scope to the identifiers
(the names of devices, users, process data entities, etc) inside it.
Solutions are used to organize deployment entities into logical groups
and prevent identity collisions.

@@

Before process data can be exposed using a web user interface the data
source must be associated with an appropriate solution and validated to
make sure that the security rules are not violated. It is hard to assume
that the security rules governing the cyber-physical system may also
apply to the cloud-based services. In the gateway scenario, they can be
mapped on each other or entirely independent. The
\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
service for \texttt{IoT\ Hub} that enables devices' connection process
management, upon device providing valid identity attestation it assigns
the device to an appropriate \texttt{IoT\ Hub} instance and returns to
the device connection parameters, which allow direct connection with
given \texttt{IoT\ Hub} service. The device proceeds to use the same
attestation in \texttt{IoT\ Hub} connection and based on it, is granted
authorization to selected resources and operations including but not
limited to data transfer updating the user interface.

@@

\begin{itemize}
\tightlist
\item
  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a
  factory network and register them in Azure IoT Hub implemented using
  \texttt{IoT\ Edge}
\item
  \texttt{Digital\ Twins} - managing the graph of digital twins, which
  are to represent some real-world process or entity
\end{itemize}

@@

Having defined types in advance, a gateway may provide dedicated
conversions functionality, i.e.~replacing bitstream used by the
cyber-physical system by equivalent one for the cloud-based services.
The Azure offers a vast variety of built-in types ready to be used in
common cases, but not necessarily there are equivalent counterparts in
use by the cyber-physical system. Additionally, the data conversion must
address the following issues:

@@

In \texttt{IoT\ Central} a cyber-physical system is represented as a set
of devices. The characteristics and behaviors of each device kind are
described by the device template. This Device Template (DT) contains
also metadata describing the data (called telemetry) exchanged over the
wire with the cyber-physical system called Device Capability Model
(DCM). Additionally, the DT contains properties, customization, and
views definitions used by the service locally. As an option, DCM
expressed as a JSON-LD can be imported into a Device Template.
\texttt{IoT\ Central} allows also to create and edit a DCM using the
dedicated web UI. A JSON file containing DCM can be derived from an
information model used as a foundation to establish the semantic-context
applied to achieve interoperability of the devices interconnected as the
cyber-physical system. DCM development against any external information
model is a design-time task and should be supported by dedicated
development tools. In any case, the data interchanged between the cloud
and the gateway must be compliant with the DCM, hence the middleware
software must be aware of conversions that must be applied to achieve
this interoperability.

@@

\begin{itemize}
\tightlist
\item
  \texttt{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure IoT Hub
\item
  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
  Device and Service SDKs
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
  Device Client SDK for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} -
  Provisioning Device Client AMQP Transport for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Http} -
  Provisioning Device Client Http Transport for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} -
  Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}

>>>>

Deployment of the hybrid solution providing interoperability of the
\textbf{machine-centric} cyber-physical systems designed atop of M2M
reactive communication and emerging cloud computing as a
\textbf{human-centric} front-end requires decisions addressing the
selection of the services supporting web user interface capable to
expose process data. In this context, the service is any
autonomous (with own identity) software component or module that is
interfacing with selected cyber-physical systems for data collection,
analysis, and also remote control. Microsoft Azure is a cloud-based
product. It offers a vast variety of services. This virtual environment
handles an unlimited number of users and devices organized using a
solution concept. The solution aggregates users, devices, services, and
required additional resources scoping on a selected scenario. The
solution serves as a context that provides a scope to the identifiers
(the names of devices, users, process data entities, etc) inside it.
Solutions are used to organize deployment entities into logical groups
and prevent identity collisions.

@@

Before process data can be exposed using a web user interface the data
source must be associated with an appropriate solution and validated to
make sure that the security rules are not violated. It is hard to assume
that the security rules governing the cyber-physical system may also
apply to the cloud-based services. In the gateway scenario, they can be
mapped on each other or entirely independent. The
\texttt{IoT\ Hub\ Device\ Provisioning\ Service} (DPS) is a helper
service for \texttt{IoT\ Hub} that enables devices' connection process
management, upon device providing valid identity attestation it assigns
the device to an appropriate \texttt{IoT\ Hub} instance and returns to
the device connection parameters, which allow direct connection with
given \texttt{IoT\ Hub} service. The device proceeds to use the same
attestation in \texttt{IoT\ Hub} connection and based on it, is granted
authorization %MP authorization can be applied only to operations ?% to selected resources and operations including but not
limited to data transfer updating the user interface.

@@

\begin{itemize}
\tightlist
\item
  \texttt{Industrial\ IoT} - discovering OPC UA enabled servers in a factory network and register them in Azure \texttt{IoT\ Hub} implemented using \texttt{IoT\ Edge}
\item
  \texttt{Digital\ Twins} - managing the graph of digital twins, which are to represent some real-world process or entity
\end{itemize}

@@

Having defined types in advance, a gateway may provide dedicated conversions functionality, i.e.~replacing bitstreams used by the cyber-physical system by equivalent ones for the cloud-based services. The Azure offers a vast variety of built-in types ready to be used in common cases, but not necessarily there are equivalent counterparts in use by the cyber-physical system. Additionally, the data conversion must address the following issues:

@@

In \texttt{IoT\ Central} a cyber-physical system is represented as a set
of devices. The characteristics and behavior of each device kind are
described by the device template. This Device Template (DT) contains
also metadata describing the data (called telemetry) exchanged over the
wire with the cyber-physical system called Device Capability Model
(DCM). Additionally, the DT contains properties, customization, and
views definitions used by the service locally. As an option, DCM
expressed as a JSON-LD can be imported into a Device Template.
\texttt{IoT\ Central} allows also to create and edit a DCM using the
dedicated web UI. A JSON file containing DCM can be derived from an
information model used as a foundation to establish the semantic-context
applied to achieve interoperability of the devices interconnected as the
cyber-physical system. DCM development against any external information
model is a design-time task and should be supported by dedicated
development tools. In any case, the data interchanged between the cloud
and the gateway must be compliant with the DCM, hence the middleware
software must be aware of conversions that must be applied to achieve
this interoperability.

@@

\begin{itemize}
\tightlist
\item
  \texttt{Microsoft.Azure.Devices} - Service SDK for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Client}- Device SDK for Azure \texttt{IoT\ Hub}
\item
  \texttt{Microsoft.Azure.Devices.Shared} - Common code for Azure IoT
  Device and Service SDKs
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Client} - Provisioning
  Device Client SDK for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Amqp} -
  Provisioning Device Client AMQP Transport for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Http} -
  Provisioning Device Client Http Transport for Azure IoT Devices
\item
  \texttt{Microsoft.Azure.Devices.Provisioning.Transport.Mqtt} -
  Provisioning Device Client MQTT Transport for Azure IoT Devices
\end{itemize}
